UMD Building Classification Proposal

### 2024-12-08 report/paper/draft.tex
paper to local

\begin{itemize}
    \item On the topic of image recognition/classification, AlexNet, VGG, and Resnet are strong examples of traditional CNN recognition and classification models. We intend to build on their techniques.
    \item With respect to image segmentation, we may end up using Grad-CAM/Score-CAM as detailed after this section. However, we will compare with traditional segmentation techniques as detailed in class (proposals and culling, and we can implement something similar to U-Net)
\end{itemize}

@@

@@

\begin{itemize} % IP: Gradcam, Scorecam, Gradcam++
    \item Grad-CAM, Selvaraju, et al.\ (2019), uses the final gradient into the last convolution layer to produce a visual representation of strength in decision making. This is a visual indicator of model strength and is on paper highly useful for highlighting image classification confidence, but can also be used to help define segmentation. 
    % https://arxiv.org/abs/1610.02391 gradcam
    \item Grad-CAM++, Chattopadhay, et al.\ (2018) is an upgrade to Grad-CAM by generalizing it. It can then isolate/identify multiple object instances in a single image (important for our proposal due to the presence of multiple buildings in images) and a generally improved visual indicator. 
    % https://arxiv.org/abs/1710.11063 gradcam++
    \item Score-CAM, Wang, et al.\ (2020) is an alternative approach to Grad-CAM that completely discards using the gradient and instead evaluates the weight of each activation map in the forward pass. 
    % https://arxiv.org/abs/1910.01279 scorecam
\end{itemize}

@@

>>>>

\begin{itemize}
    \item On the topic of image recognition/classification, AlexNet, VGG, and Resnet are strong examples of fully supervised traditional CNN recognition and classification models. 
    \item With respect to image segmentation, we end up using Grad-CAM/Score-CAM as detailed after this section.
\end{itemize}

@@

We prioritized utilizing Semi-Supervised Methods of image recognition. For this, we used FixMatch and MeanTeach methods.

@@

\begin{itemize} % IP: Gradcam, Scorecam, Gradcam++
    \item \citet{selvaraju} Grad-CAM, Selvaraju, et al.\ (2019), uses the final gradient into the last convolution layer to produce a visual representation of strength in decision making. This is a visual indicator of model strength and is on paper highly useful for highlighting image classification confidence, but can also be used to help define segmentation. 
    % https://arxiv.org/abs/1610.02391 gradcam
    \item Grad-CAM++, Chattopadhay, et al.\ (2018) is an upgrade to Grad-CAM by generalizing it. It can then isolate/identify multiple object instances in a single image (important for our proposal due to the presence of multiple buildings in images) and a generally improved visual indicator. 
    % https://arxiv.org/abs/1710.11063 gradcam++
    \item Score-CAM, Wang, et al.\ (2020) is an alternative approach to Grad-CAM that completely discards using the gradient and instead evaluates the weight of each activation map in the forward pass. 
    % https://arxiv.org/abs/1910.01279 scorecam
\end{itemize}

@@

% https://www.getbibtex.com
